PeakNet: An Autonomous Bragg Peak Finder with Deep Neural Networks

### 2023-06-16 manuscript.tex
Add more discussion on alpha in focal loss.

where CFL stands for categorical focal loss, $\alpha_j$ is a balancing factor
for each class, $y_j^{(i)}$ is the grouth truth label of the $j$-th class for
the $i$-th example.  $p_j^{(i)}$ is the predicted probability of the $j$-th
class for the $i$-th example, calculated by the neural network $f$ parameterized
by $\theta$ given input $x_j^{(i)}$.  $\gamma$ is a parameter controling the
extent to which the weight of well-classified examples, such as background
pixels, is reduced.  In our neural network training, we chose $\alpha = 1.2$
across all examples and $\gamma = 2.0$.  Essentially, this means $(1-\hat{p}
_j^{(i)}) ^\gamma$ is solely responsible for down-weighting easy examples, as
$\hat{p} _j^{(i)}$ is usually large in this case.

>>>>

where CFL stands for categorical focal loss, $\alpha_j$ is a balancing factor
for each class, $y_j^{(i)}$ is the grouth truth label of the $j$-th class for
the $i$-th example.  $p_j^{(i)}$ is the predicted probability of the $j$-th
class for the $i$-th example, calculated by the neural network $f$ parameterized
by $\theta$ given input $x_j^{(i)}$.  $\gamma$ is a parameter controling the
extent to which the weight of well-classified examples, such as background
pixels, is reduced.  In our neural network training, we chose $\gamma = 2.0$,
essentially, this means $(1-\hat{p} _j^{(i)}) ^\gamma$ is solely responsible for
down-weighting easy examples, as $\hat{p} _j^{(i)}$ is usually large in this
case.  Finding the ideal values for $\alpha$ can be a delicate process with only
marginal returns, as highlighted in the original focal loss study
\citep{linFocalLossDense2018}.  In order to fully utilize focal loss, we decided
to use a fixed trivial value of $\alpha = 1.2$ for all examples, primarily for
the sake of completeness.  This choice essentially treats $\alpha$ as a simple
scaling factor without significant impact.  It is worth noting that in most
cases, the sum of all $\alpha_j$ values, denoted as $\sum_{j = 1}^{C} \alpha_j$,
is expected to equal 1.
